GO

### 2020-01-22 analysis/12_GO.Rmd
new candidate genes

---
title: "GO"
output: html_document
---

@@

```{r}
candidates <- c(  "PRLR", 
                 "AVP", "VIP", "AVPR1A", "AVPR1B", "OXT", 
                 "GNRH1", "NPY",
                "CRH", "FSHB", "GH", 
                 "JAK2", "HCRT", "TRH", "TSHB",
                "LH", "FSH",
                "MC3R", "MC4R", "MC5R", 
                "ESR1", "ESR2", "AR", 
                "STAT5B", "CISH")
candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidategenes"
candidates <- candidates %>% select(GO, gene)

@@

```{r}
candidates <- c( "PRL", "PRLR", 
                 "AVP", "VIP", "AVPR1A", "AVPR1B", "OXT", 
                 "GNRH1", "GNRHR", "NPY",
                "CRH", "FSHB", "GH", 
                 "JAK2", "HCRT", "POMC", "TRH", "TSHB",
                "LH", "FSH",
                "POMC", "MC3R", "MC4R", "MC5R", 
                "ESR1", "ESR2", "AR", 
                "STAT5", "CISH")
candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidate genes"

candidate_DEGs <- left_join(candidates, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>%
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9"))
candidate_DEGs <- as.data.frame(candidate_DEGs)
row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
candidate_DEGs <- tail(candidate_DEGs,10)
kable(candidate_DEGs)

>>>>

---
title: "GO"
output: md_document
---

@@

```{r}
candidates <- c("PRL", "PRLR", 
                 "AVP", "VIP", "AVPR1A", "AVPR1B", "OXT",  "VIPR1", "VIPR2",
                "GNRH1", "NPY", "LH", "FSH",
                "CRH", "FSHB", "GH",  "JAK2", "HCRT", "TRH", "TSHB",
                "MC3R", "MC4R", "MC5R",  "NR3C1", "NR3C2",
                "ESR1", "ESR2", "AR", 
                "STAT5B", "CISH",
                "GNRHR", "NPVF")

candidates <- as.data.frame(candidates)
names(candidates)[1] <- "gene"
candidates$GO <- "candidategenes"
candidates <- candidates %>% select(GO, gene)

@@

```{r}
candidate_DEGs <- left_join(candidates, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>%
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9"))
candidate_DEGs <- as.data.frame(candidate_DEGs)
row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
candidate_DEGs <- tail(candidate_DEGs,10)
kable(candidate_DEGs)
